---
title: "biost561fp"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    theme: united
vignette: >
  %\VignetteIndexEntry{biost561fp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(biost561fp)
library(GA)
```
__Introduction__
The biost561fp package provides tools to solve the Traveling Salesperson Problem (TSP) using various heuristic methods. This vignette demonstrates how to generate a random distance matrix, solve the TSP using different algorithms, and compare the results.

__Generating a Random Distance Matrix__
First, we generate a random distance matrix using the generateRandomDistMatrix function. This matrix represents the distances between cities.
```{r}
# Set seed for reproducibility
set.seed(123)

# Number of cities
numCities <- 5

# Generate random distance matrix
distMatrix <- generateRandomDistMatrix(numCities)
print(distMatrix)
```

__Solving the TSP using Nearest Neighbor Algorithm__
Next, we solve the TSP using the nearest neighbor heuristic with the nearestNeighbor function.

```{r}
# Solve TSP using nearest neighbor algorithm
nn_result <- nearestNeighbor(distMatrix)
print(nn_result)
```
__Solving the TSP using Genetic Algorithm__
We also solve the TSP using a genetic algorithm with the geneticAlgorithm function.

```{r}
# Solve TSP using genetic algorithm
ga_result <- geneticAlgorithm(distMatrix)
print(ga_result)
```
__Finding the Best Solution__
Finally, we find the best solution using the solveTSP function, which compares the results of the nearest neighbor and genetic algorithms and returns the best one.

```{r}
# Find the best solution using all methods
best_solution <- solveTSP(distMatrix)
print(best_solution)
```
__Summary__
In this vignette, we demonstrated how to generate a random distance matrix, solve the TSP using the nearest neighbor and genetic algorithms, and find the best solution using the solveTSP function. The tspSolver package provides a simple and effective way to solve the Traveling Salesperson Problem using various heuristic methods.
```
